---
title: "Getting Started with binomial"
author: "Ranqi Zhong"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE, message = FALSE}

knitr::opts_chunk$set(collapse = T, comment = "#>")

library(binomial)

```


1.3) Function bin_choose()
Use factorial() to write a main function bin_choose() that calculates the number of
combinations in which k successes can occur in n trials.
```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```

1.4) Function bin_probability()
Use bin_choose() to create a main function bin_probability().
bin_probability() should take three arguments: success, trials, and prob.
Use check_trials() to check that trials is valid
Use check_prob() to check that prob is valid
Use check_success() to check that success is valid
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
bin_probability(success = 55, trials = 100, prob = 0.45)
```

1.5) Function bin_distribution()
Use bin_probability() to create a main function bin_distribution().
There are two arguments trials, and prob.
The returned output should be a data.frame with two classes: c("bindis",
"data.frame")
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

Function plot.bindis()
There is a plotting method (i.e. a function) plot.bindis() that graphs a barplot to display
the probability histogram of a binomial distribution object "bindis".
```{r}
plot(bin_distribution(trials = 5, prob = 0.5))
```

1.6) Function bin_cumulative()
Use bin_cumulative() to create a main function bin_cumulative().
This function should have two arguments trials, and prob.
The returned output should be a data.frame with two classes: c("bincum",
"data.frame")
This function should return a data frame with both the probability distribution and the
cumulative probabilities: sucesses in the first column, probability in the second column,
and cumulative in the third column.

```{r}
bin_cumulative(trials = 5, prob = 0.5)
```
```{r}
plot(bin_cumulative(trials = 5, prob = 0.5))
```

Function plot.bi() Function bin_variable()
Another function to include in your "binomial" package is bin_variable().
This is a main function that takes two arguments: trials and prob
This function should return an object of class "binvar", that is, a binomial random
variable object.
This function should invoke check_trials() and check_prob()
The returned object should be a list with named elements:
  trials: number of trials
  prob: probability of success

```{r}
bin1 <- bin_variable(trials = 10, prob = 0.3)
bin1
```

Methods summary.binvar() and print.summary.binvar()
To get a full summary description of an object "binvar",it is needed to create a function
summary.binvar().
This function takes an object of class "binvar"
The returned output is a list of class "summary.binvar" containing named elements:
  trials: number of trials
  prob: probability of success
  mean: mean or expected value
  variance: variance
  mode: mode
  skewness: skewness
  kurtosis: kurtosis
```{r}
summary(bin_variable(trials = 10, p = 0.3))
```

1.8) Functions of measures
Finally, "binomial" package should also contain main functions for each of the summary
measures: e.g. bin_mean(), bin_variance(), etc.
These are main functions that take two arguments: trials and prob
Use check_trials() to check that trials is valid
Use check_prob() to check that prob is valid
Invoke your auxiliary functions to do the corresponding calculation. For instance:
aux_mean() gets called by bin_mean().
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
